### 2021-04-08 Chapter-5/Chapter-5.tex
Updates from Overleaf

Second, many precise side-channel analysis tools rely on some techniques like symbolic executions, taint analysis, and abstract interpretations~\cite{wang2017cached,doychev2015cacheaudit,brotzman2019casym,wang2019identifying}. Those methods need to consider the semantics of each ISA instruction, which is tedious. So they build the tool on the top of existing binary analysis frameworks. Due to the limitations of binary analysis frameworks, it is hard to apply existing methods to analyze side-channels in non-cryptography libraries. For many other applications like machine learning, media, and graphic libraries built on the top architecture-dependent libraries (e.g., Intel MKL~\cite{wang2014intel}), those tools can not handle it. Moreover, existing binary analysis frameworks (e.g., Angr~\cite{shoshitaishvili2016state}) are limited to analyze floating-point instructions. But the functionality of those applications heavily depends on floating-point calculations.

Third, while many existing works can detect side-channel leakages, few of them can assess how severity level of those vulnerabilities~\cite{wang2017cached,doychev2015cacheaudit,brotzman2019casym,wang2019identifying,weiser2018data,wichelmann2018microwalk}. There are some tools~\cite{doychev2015cacheaudit,chattopadhyay2019quantifying} that can quantify the information leakage.  Those tools usually rely on the abstraction to give an upper bound estimation of each leakage site, which is useful to justify the software is secure if the reported leakage is zero. But those tools can not tell software developers how serious each leakage site would be because of the over-approximation they apply when they estimate the amount of leakage. The best way to estimate each leakage's severe level is to exploit the leakage and recover the information. However, the process itself is very tedious and needs a lot of domain knowledge.

>>>>

Second, many side-channel leakage detection tools rely on some techniques like symbolic executions, taint analysis, and abstract interpretations~\cite{203878,182946,Brotzman19Casym,236338}. Those methods need to consider the semantics of each ISA instruction, which is tedious. So they build the tool on the top of existing binary analysis frameworks. Due to the limitations of binary analysis frameworks, it is hard to apply existing methods to analyze side-channels in non-cryptography libraries. For many other applications like machine learning, media, and graphic libraries built on the top architecture-dependent libraries (e.g., Intel MKL~\cite{wang2014intel}), those tools can not handle it. Moreover, existing binary analysis frameworks (e.g., Angr~\cite{shoshitaishvili2016state}) are limited to analyze floating-point instructions. But the functionality of those applications heavily depends on floating-point calculations.

Third, while many existing works can detect side-channel leakages, few of them can assess how severity level of those vulnerabilities~\cite{203878,182946,Brotzman19Casym,236338,217537,Wichelmann:2018:MFF:3274694.3274741}. There are some tools~\cite{182946,Chattopadhyay:2017:QIL:3127041.3127044} that can quantify the information leakage.  Those tools usually rely on the abstraction to give an upper bound estimation of each leakage site, which is useful to justify the software is secure if the reported leakage is zero. But those tools can not tell software developers how serious each leakage site would be because of the over-approximation they apply when they estimate the amount of leakage. The best way to estimate each leakage's severe level is to exploit the leakage and recover the information. However, the process itself is very tedious and needs a lot of domain knowledge.
